Left-linear rules in adhesive categories

### 2024-02-16 icalp/fusione.tex
typo

\begin{lemma}
  \label{le:switchC}
  Let $\der{D}_i$ for $i \in \interval[0]{n+1}$ be derivation sequences
  and consider a switching sequence
  \begin{center}
    $\der{D}_0 \shift{\nu_0} \der{D}_1 \shift{\nu_1} \ldots
     \der{D}_n \shift{\nu_n} \der{D}_{n+1}$
  \end{center}
  AIf the subsequence starting from $\der{D}_1$ consists of
  inversions and $\nu_0=\transp{i}$ while
  $\nu_n = \transp{\nu_{1,n}(i)}$, then there is shorter switching sequence
  consisting only of inversions
  \begin{center}
    $\der{D}_0 \equiv_a \der{D}_0' \shift{\nu_2'} \der{D}_3' \shift{\nu_3'} \ldots
    \shift{\nu_{n-1}'} \der{D}_n'$
  \end{center}
\end{lemma}

>>>>

\begin{lemma}
  \label{le:switchC}
  Let $\der{D}_i$ for $i \in \interval[0]{n+1}$ be derivation sequences
  and consider a switching sequence
  \begin{center}
    $\der{D}_0 \shift{\nu_0} \der{D}_1 \shift{\nu_1} \ldots
     \der{D}_n \shift{\nu_n} \der{D}_{n+1}$
  \end{center}
  If the subsequence starting from $\der{D}_1$ consists of
  inversions and $\nu_0=\transp{i}$ while
  $\nu_n = \transp{\nu_{1,n}(i)}$, then there is shorter switching sequence
  consisting only of inversions
  \begin{center}
    $\der{D}_0 \equiv_a \der{D}_0' \shift{\nu_2'} \der{D}_3' \shift{\nu_3'} \ldots
    \shift{\nu_{n-1}'} \der{D}_n'$
  \end{center}
\end{lemma}
